### 2023-04-09 reachable-resilience.tex
details
up

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & $\emptyset $ & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable (Thm~\ref{srp down up})  & Decidable (Thm~\ref{downward srp})  & Decidable (Thm~\ref{downward srp}) \\ \hline
   BSRP & ??  &  ??  & Decidable (Prop~\ref{downward brp}) \\ \hline
      kSRP & ??  & ?? & Decidable (Prop~\ref{downward brp}) \\ \hline
 \end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis &  none  & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable (Thm~\ref{srp down up})  & Decidable (Thm~\ref{downward srp})  & Decidable (Thm~\ref{downward srp}) \\ \hline
   BSRP & ??  &  ??  & Decidable (Prop~\ref{downward brp}) \\ \hline
      kSRP & ??  & ?? & Decidable (Prop~\ref{downward brp}) \\ \hline
 \end{tabular}
\end{center}
% \alain{une hypothèse n'est pas l'ensemble vide}
